Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-02 main.tex
General experimental setup

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Robotic System}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation of the Interaction}

Figure~\ref{experimental_setup} illustrates our general experimental setup: a
face-to-face child-robot interaction with an (autonomous) Aldebran's Nao robot.

A tactile tablet (with a custom application) is used for both the robot and the
child to write: during a typical round, the child requests the robot to write
something (a single letter, a number or a full word), and push the tablet
towards the robot, the robot writes on the tablet by gesturing the writing, but
\emph{without actually physically touching the tablet}), the child then pull
back the tablet, correct the robot's attempt by writing him/herself on top or
next to the robot's writing (see the picture in Figure~\ref{fig:diego}), and
``send'' his/her demonstration to the robot by pressing a small button on the
tablet. The robot ``learns'' from this demonstration and tries again.

Since the child is assumed to take on the role of the teacher, we had to ensure
he/she would be able to manage by him/herself the turn-taking and the overall
progression of the activity (moving to the next letter or word). In our design,
the turn-taking relies on the robot prompting for feedback once it is done with
its writing (simple sentences like ``What do you think?''), and pressing on a
small robot icon on the tablet once the child has finished correcting. In our
experiments, both were easy to grasp for children.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{experimental_setup}
    \caption{Our experimental setup: face-to-face interaction with a Nao robot.
    The robot writes on the tactile tablet, the child then corrects the robot by
    directly overwriting its letters on the tablet, with a stylus directly. An adult
    (either a therapist or an experimenter, depending on the studies), remains next
    to the child to guide the work (prompting, turn taking, etc.).}
    \label{experimental_setup}
\end{figure}

Implementing such a system raises several challenges: first, acquiring,
analyzing and learning from hand-written demonstration lays at the core of the
our approach and we developed several algorithms for the robot to generate
initial bad writing and to respond in an adequate manner, showing visible (but
not too quick) writing improvements.

Then, the actual implementation on the robot required the coordination of
several modules (from performing gestures and acquiring the user's input to
the high-level state machine), spread over several machines (the robot itself,
one laptop and up to four tactile tablets for certain studies we conducted). We
relied on ROS to ensure the synchronization and communication between these
modules.

Finally, the interaction itself, involving a robot, one or two children and, in
one study, an occupational therapist, also raised by itself several challenges.

We detail each of these points in the following sections.
